Tulai

### 2023-09-29 paper/paper.qmd
remove function conflicts where multiple packages have functions of the same name

```{r}
# load libraries
library(tidyverse)
library(here)
library(ggpmisc)
library(ggrepel)
library(ggbeeswarm)
library(cowplot)
library(knitr)
library(ggcorrplot)
library(ggpubr)
library(ggbiplot)
```

@@

# take a look
 rev(sort(table(tl_final$core)))
 rev(sort(table(tl_final$corefrag)))
 rev(sort(table(tl_final$`core-fragment`)))
 rev(sort(table(tl_final$`core-typology`)))
 rev(sort(table(tl_final$blank)))
```

>>>>

```{r}
# load libraries
library(here)
library(ggpmisc)
library(ggrepel)
library(ggbeeswarm)
library(cowplot)
library(knitr)
library(ggcorrplot)
library(ggpubr)
library(ggbiplot)
library(tidyverse) # load this last to minimize conflicts
```

@@

# take a look
 # rev(sort(table(tl_final$core)))
 # rev(sort(table(tl_final$corefrag)))
 # rev(sort(table(tl_final$`core-fragment`)))
 # rev(sort(table(tl_final$`core-typology`)))
 # rev(sort(table(tl_final$blank)))
```
